Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-02 slides/slides.tex
for presentation

\begin{frame}[fragile]{Macro-based compilation}
    Anglican code macro-compiled into Clojure:
    \begin{minipage}{0.48\textwidth}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(loop [data data]
  (if (seq data)
    (let [[x & data] data]
      (observe (gamma a b) x)
      (recur data))
    (predict :a a)))
\end{minted}
    \end{minipage}
    \begin{minipage}{0.44\textwidth}
    \vspace{2em}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(fn loop [C23151 $state data]
   (if (seq data)
     (let [[x & data] data]
       (->observe 'O23153 (gamma a b) x
         (fn do23152 [_ $state]
           (loop C23151 $state data))
         $state))
     (fn []
       (C23151
         nil
         (add-predict $state :a a)))))
\end{minted}
    \end{minipage}
\end{frame}

@@

\begin{frame}{Other inference algorithms}
    \begin{itemize}
        \item Implement \texttt{infer}.
        \item Redefine one or both checkpoints.
        \item An average implementation is $\approx 150$ lines of source
            code.
        \item A dozen different inference algorithms are in the
            code base.
        \item Half of them are really useful.
    \end{itemize}
\end{frame}

>>>>

\begin{frame}[fragile]{Macro-based compilation}
    Anglican code macro-compiled into Clojure, in CPS:
    \begin{minipage}{0.48\textwidth}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(loop [data data]
  (if (seq data)
    (let [[x & data] data]
      (observe (gamma a b) x)
      (recur data))
    (predict :a a)))
\end{minted}
    \end{minipage}
    \begin{minipage}{0.44\textwidth}
    \vspace{2em}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(fn loop [C23151 $state data]
   (if (seq data)
     (let [[x & data] data]
       (->observe 'O23153 (gamma a b) x
         (fn do23152 [_ $state]
           (loop C23151 $state data))
         $state))
     (fn []
       (C23151
         nil
         (add-predict $state :a a)))))
\end{minted}
    \end{minipage}
	\bigskip

	A continuation accepts \textit{two} arguments:
	\begin{itemize}
		\item The computed value.
		\item The internal state (\texttt{\$state}).
	\end{itemize}
	Functions accept continuation and state as two first arguments.
\end{frame}

@@

\begin{frame}{Other inference algorithms}
    \begin{itemize}
        \item Implement \texttt{infer}.
        \item Redefine one or both checkpoints.
        \item An average implementation is $\approx 150$ lines of Clojure
            code.
        \item A dozen different inference algorithms are in the
            code base.
        \item Half of them are really useful.
    \end{itemize}
\end{frame}
